{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
Paper work 3.2

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure.\\
	Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

	\begin{equation}
		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	All functions $f$ satisfying the above condition are called square-integrable functions. Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined.\\
	Its inner product is defined as

@@

	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.

@@

	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

@@

	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.

>>>>

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

	\begin{equation}
		\lvert \lvert f \rvert \rvert^2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	All functions $f$ satisfying the above condition are called square-integrable functions. Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined. Its inner product is defined as

@@

	 $\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval $[0,1]$ for the purpose of this paper. The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

@@

@@

	where $\Omega$ is a sample space. The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
